Models

### 2023-10-03 analysis/models.qmd
bayes

library(tidyverse)
library(marginaleffects)
library(brms)
library(ggplot2)
library(ggdist)
library(broom)
library(here)

data <- read_csv(here("data", "all.csv"))

@@

## Estimate the Causal Effect

First let's do a replication of the INTERACT re-analysis.

@@

priors <- c(prior(normal(0, 1.5), class = Intercept))

inits <- list(Intercept = c(-2, -1, 0, 1, 2, 2.5))

mod <- brm(mrs_90 ~ 1,
  data = data,
  family = cumulative("logit"),
  prior = priors,
  init = rep(list(inits), 4),
  chains = 4, iter = 5000 * 2, seed = 28203, cores = 4,
  backend = "cmdstanr", refresh = 0
)

@@

## Conduct Sensitivity Analyses

>>>>

library(tidyverse)
library(ordinal)
library(marginaleffects)
library(modelsummary)
library(brms)
library(tidybayes)
library(broom.mixed)
library(ggplot2)
library(ggdist)
library(broom)
library(here)

data <- read_rds(here("data", "all.rds"), refhook = NULL)

# plot stuff
theme_set(theme_minimal(base_family = "Cantarell"))

# convert mrs to ordered factors
mrs_levels <- c("0", "1", "2", "3", "4", "5", "6")

data <- data |>
  mutate(
    mrs_30 = fct_inseq(as.character(mrs_30), ordered = TRUE),
    mrs_90 = fct_inseq(as.character(mrs_90), ordered = TRUE),
    mrs_180 = fct_inseq(as.character(mrs_180), ordered = TRUE),
    mrs_270 = fct_inseq(as.character(mrs_270), ordered = TRUE),
    mrs_365 = fct_inseq(as.character(mrs_365), ordered = TRUE),
  ) |>
  filter(ich_location == "Basal Ganglia" | ich_location == "Thalamus" | ich_location == "Lobar")

@@

## Visualization

@@

mrs_prop <- data |>
  count(mrs_90) |>
  mutate(p = n / sum(n), cumsum_p = cumsum(p)) |>
  na.omit()

mrs_prop |>
  ggplot(aes(x = mrs_90, y = p)) +
  geom_col(fill = "coral") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "mRS 90", y = "Proportion")

mrs_prop |>
  ggplot(aes(x = as.integer(mrs_90), y = cumsum_p)) +
  geom_point(size = 2) +
  geom_line(linewidth = 1) +
  labs(x = "mRS 90", y = "Cumulative Proportion")

mrs_prop |>
  ggplot(aes(x = as.integer(mrs_90), y = log(cumsum_p) - log(1 - cumsum_p))) +
  geom_point(size = 2) +
  geom_line(linewidth = 1) +
  labs(x = "mRS 90", y = "Logit Cumulative Proportion")

@@

## Frequentist Analysis

### Mediation Analysis with Neurosurgery and ICH Laterality

```{r frequentist ordinal}

mrs_90_ich_lat <- clm(
  mrs_90 ~ ich_laterality,
  data = data,
  link = "logit"
)

neurosurg_ich_lat <- clm(
  neurosurgery_evac ~ ich_laterality,
  data = data,
  link = "logit"
)

mrs_90_ich_lat_neurosurg <- clm(
  mrs_90 ~ ich_laterality + neurosurgery_evac,
  data = data,
  link = "logit"
)

summary(mrs_90_ich_lat)
summary(neurosurg_ich_lat)
summary(mrs_90_ich_lat_neurosurg)

## Bayesian Analysis

```{r bayesian ordinal}

fit1 <- brm(
  data = data,
  family = cumulative(probit),
  mrs_90 ~ 1,
)

fit2 <- brm(
  data = data,
  family = cumulative(logit),
  mrs_90 ~ 1,
)

fit3 <- brm(
  data = data,
  family = cumulative(logit),
  mrs_90 ~ ich_laterality,
)

print(fit1)
print(fit2)
print(fit3)

pred <- predictions(fit3)
